---
title: "Application on Data Retrieval from Twitter"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Claimer: This training is obtained from the following source:
https://raw.githubusercontent.com/maria-pro/useR2019_tutorial/master/Twitter.Rmd 
and is modified as needed.


### Package `rtweet` 

The dataset that we are going to work with is for coffee!

Now, lets load tweets, previously saved in the `coffeeTweets.csv` file using `read_csv` function. 

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(readr)
data <- read_csv("data/coffeeTweets.csv")
View(data)
glimpse(data)
```

## Hashtag frequency 

Let's investigate which other hashtags were used in tweets that we located and the frequency of those hashtags:

The hashtag information is stored in the `hashtag` variable. Let's have a look at them

We will convert all hashtags to lower case first and then use a `wordcloud` to show the frequencies

```{r}
data %>% 
  pull(hashtags) %>% 
  head()
```

```{r}
library(forcats)
library(tidytext)

tidy_hashtags <- data %>%
  select(hashtags)%>%
  unnest_tokens(output=Word, hashtags, token = "words")%>% #tokenize hashtags by word
  count(Word) %>% #we have two variable, word and n.
  filter(n > 500) %>% #there are 26 words
  arrange(desc(n)) %>% 
  rename(freq = n)

tidy_hashtags
```

```{r}
library(wordcloud2)
wordcloud2(tidy_hashtags)
```
  
or we can go fancy with `color` and `shape` parameters:
  
```{r}
wordcloud2(tidy_hashtags, size = 2, shape="star", color = "random-light")
```


# Not in class.
# Emojis

`Emoji` are smileys used in `Twitter` and communications.They are numerous and fun! They are  like emoticons, but emoji are actual pictures instead of typographics. 

We will use `hadley/emo` package

```{r eval=FALSE}
devtools::install_github("hadley/emo")
library(emo)
```

They are fun:

emo::ji("heart")

emo::ji("ghost")

Let's have a look how we can use them to analyse tweets:

Let's first extract them from tweets into a separate column `emoji and `unnest` them

```{r eval=FALSE}
library(stringr)

emoji <- data %>%
  mutate( 
    emoji = ji_extract_all(text)
  ) %>%
  select(screen_name,emoji) %>% 
  unnest(emoji) 
emoji
```
